The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources

### 2019-11-09 paper.tex
Modified title page to use MNRAS template.  There's more to fix in order to get it MNRAS-ready

%\documentclass[english, apj]{emulateapj}
\documentclass[english, backref,breaklinks,colorlinks,citecolor=blue, usenatbib]{mnras}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amstext}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
%\usepackage[nobottomtitles]{titlesec}
\usepackage{array}
\usepackage{rotating}
\usepackage{units}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{url}
\usepackage{babel}
\usepackage{float}
\usepackage{savesym}
\savesymbol{tablenum}
\usepackage{siunitx}
\restoresymbol{SIX}{tablenum}
%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
\usepackage{hyperref}
\usepackage{hypcap}

\makeatletter

\newcommand{\msun}{\mbox{$\,{\rm M}_\odot$}}

\sloppy

\providecommand{\tabularnewline}{\\}
% Alter some LaTeX defaults for better treatment of figures:
    % See p.105 of "TeX Unbound" for suggested values.
    % See pp. 199-200 of Lamport's "LaTeX" book for details.
    %   General parameters, for ALL pages:
    \renewcommand{\topfraction}{0.9}	% max fraction of floats at top
    \renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
    %   Parameters for TEXT pages (not float pages):
    \setcounter{topnumber}{2}
    \setcounter{bottomnumber}{2}
    \setcounter{totalnumber}{4}     % 2 may work better
    \setcounter{dbltopnumber}{2}    % for 2-column pages
    \renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
    \renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
    %   Parameters for FLOAT pages (not text pages):
    \renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
	% N.B.: floatpagefraction MUST be less than topfraction !!
    \renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages

	% remember to use [htp] or [htpb] for placement

\begin{document}

\title{The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources}

\author{Charles Zivancev,$^{1}$ 
Jeremiah P. Ostriker,$^{1,3}$ 
Andreas H.W. K\"upper$^{1,2}$
\\
$^{1}$Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA\\
$^{2}$Hubble Fellow\\
$^{3}$Princeton University, New Jersey, USA}
\thanks{Correspondence to: csz2104@columbia.edu}

>>>>

%\documentclass[english, backref,breaklinks,colorlinks,citecolor=blue, usenatbib]{mnras}
%\usepackage{amsbsy}
%\usepackage{amsmath}
%\usepackage{amstext}
%\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
%%\usepackage[nobottomtitles]{titlesec}
%\usepackage{array}
%\usepackage{rotating}
%\usepackage{units}
%\usepackage{textcomp}
%\usepackage{graphicx}
%\usepackage{url}
%\usepackage{babel}
%\usepackage{float}
%\usepackage{savesym}
%\savesymbol{tablenum}
%\usepackage{siunitx}
%\restoresymbol{SIX}{tablenum}
%%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
%\usepackage{hyperref}
%\usepackage{hypcap}

%\makeatletter

%\newcommand{\msun}{\mbox{$\,{\rm M}_\odot$}}

%\sloppy

% mnras_guide.tex
%
% MNRAS LaTeX user guide
%
% v3.0 released 22 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0   September 2013 - May 2015
%    First version: complete rewrite of the user guide
%    Basic structure taken from mnras_template.tex by the same author

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib,useAMS]{mnras}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\kms}{\,km\,s$^{-1}$} % kilometres per second
\newcommand{\bibtex}{\textsc{Bib}\!\TeX} % bibtex. Not quite the correct typesetting, but close enough

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[MNRAS]{The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[]{
Charles Zivancev$^{1}$\thanks{Contact e-mail: \href{mailto:csz2104@columbia.edu}{csz2104@columbia.edu}},
Jeremiah Ostriker$^{1}$,
Andreas H.W. K\"upper$^{2}$
\\
% List of institutions
$^{1}$Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA\\
$^{2}$Hubble Fellow\\
}
% These dates will be filled out by the publisher
\date{Last updated 2019 Nov 09; in original form 2019 November 9}

% Enter the current year, for the copyright statements etc.
\pubyear{2019}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
